UKB Models

### 2023-10-11 proof-of-concept_mods.Rmd
working through combat for regional vols - some warninigs/errs

```{r}
sim.site.list <- c("Site_A", "Site_B", "Site_C")
n_female <- table(ukb_df_age.filt$sex)["Female"]
n_male <- table(ukb_df_age.filt$sex)["Male"]

# Sample probabilities
male_prob <- c(0.5, 0.125, 0.375)
female_prob <- c(0.5, 0.375, 0.125)

@@

ukb_df_sites <- ukb_df_age.filt %>%
  mutate(sim.site = as.factor(ifelse(sex == "Male", sampled_males, sampled_females)))
table(ukb_df_sites$sim.site, ukb_df_sites$sex)
sum(is.na(ukb_df_sites$sim.site)) #all subj assigned to sites
```

@@

# Print or display the histograms
for (pheno in vol_list_global) {
  print(global_site_plots[[pheno]])
}
```

>>>>

```{r}
set.seed(1010101)
sim.site.list <- c("Site_A", "Site_B", "Site_C")
n_female <- table(ukb_df_age.filt$sex)["Female"]
n_male <- table(ukb_df_age.filt$sex)["Male"]

# Sample probabilities
male_prob <- c(0.33, 0.0825, 0.5875)
female_prob <- c(0.33, 0.5875, 0.0825)

@@

ukb_df_sites <- ukb_df_age.filt %>%
  mutate(sim.site = as.factor(ifelse(sex == "Male", sampled_males, sampled_females)))

#write out
write_csv(ukb_df_sites, file="data/ukb_CN_data_simsites.csv")
```

```{r}
table(ukb_df_sites$sim.site)
table(ukb_df_sites$sim.site, ukb_df_sites$sex)
sum(is.na(ukb_df_sites$sim.site)) #all subj assigned to sites
anova(lm(age_days ~ sim.site, ukb_df_sites))
ukb_df_sites %>%
  group_by(sim.site) %>%
  summarise(min = min(age_days), max = max(age_days), mean = mean(age_days))
```

@@

# Print or display the histograms
for (pheno in vol_list_global) {
  print(global_site_plots[[pheno]])
}
```
## ComBat

And now, to combat the data across the simulated sites!

### 2023-10-11 ukb_curation-eda.Rmd
working through combat for regional vols - some warninigs/errs

source("/Users/megardn/Desktop/BGD_Repos/GAMLSS/plotting_functions.R")
```

@@

# Print or display the histograms
for (pheno in vol_list_global) {
  print(global_plots[[pheno]])
}
```

>>>>

source("/Users/megardn/Desktop/BGD_Repos/GAMLSS/plotting_functions.R")
source("/Users/megardn/Desktop/BGD_Repos/combat_biovar/R_scripts/gamlss_helper_funs.R")
```

@@

# Print or display the histograms
for (pheno in vol_list_global) {
  print(global_plots[[pheno]])
}

ukb_centered %>%
  dplyr::filter(sex == "Male") %>%
  select(GMV) %>%
  var()

ukb_centered %>%
  dplyr::filter(sex == "Female") %>%
  select(GMV) %>%
  var()

ukb_centered %>%
  #dplyr::filter(sex == "Male") %>%
  select(GMV) %>%
  var()
```
